Statistical paradoxes in coronavirus case-counts: selection bias, measurement error, and the COVID-19 pandemic

### 2020-08-28 write-up/covid-writeup.tex
Update covid-writeup.tex
better intro

A real-world constraint for countries, states, and municipalities is the monetary and time cost of random sampling. The second objective of this paper is to demonstrate how random samples provide necessary auxiliary information to address selection bias in coronavirus case-count data.

Using a random sample from Indiana, we construct improved  corrected estimates of the prevalence and true case-counts.  We end with several remarks on cautious use of these methods.

>>>>

Due to monetary and time constraints, random testing may be performed infrequently.  As of August 28, 2020, Indiana is the only state to conduct statewide random sample testing, which was collected from April 25--29, 2020.  Such infrequent random testing may be insufficient to understand the trajectory of infectious disease prevalence which may change rapidly over time.  Therefore, while random testing is preferred, governments, researchers, and policy makers continue to look toward the coronavirus case-counts to understand the impact of COVID-19 on the population and make data-informed decisions.

The second objective is to demonstrate how random samples provide necessary auxiliary information to address selection bias in coronavirus case-count data.  Random samples are used in estimation of selection propensities which are then employed in an inverse-probability weighting scheme to construct adjusted estimators of disease prevalence.  A doubly robust extension allows researchers to combine these estimates with epidemiological forecasts based on compartmental models common in the study .  While we demonstrate improvements over simple estimates of disease prevalence, we highlight how selection bias may persist.
